Estimating Predictive Rate-Distortion Curves via Neural Variational Inference

### 2019-05-03 paper.tex

In the neural networks literature, the most commonly used method using variational bounds similar to (\ref{eq:bound}) is the Variational Autoencoder \citep{kingma-auto-encoding-2014}, which corresponds to the setting where $\lambda=1$ and the predicted output is equal to the observed input.

>>>>

In the neural networks literature, the most commonly used method using variational bounds similar to (\ref{eq:bound}) is the Variational Autoencoder \citep{kingma-auto-encoding-2014, bowman-generating-2016}, which corresponds to the setting where $\lambda=1$ and the predicted output is equal to the observed input.
